Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-04-22 AO_bondedSi.tex
Elucidate reason we can treat the Si blocks incoherently, frame the statement in the positive.  Closes #31

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
\label{secTheory}
A pair of bonded silicon wafers or pucks with a small gap forms three coupled cavities with the air gap as the the central cavity.  The outer cavities, those within the Si, however, were not produced with coherence in mind.  Their sides are not necessarily flat and parallel to the required level and the specifics of their deviation from perfect etalons are usually not known to the level necessary to treat them as coherent structures in the analysis.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps.  In the air gap, however, the gap size is small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the thick Si substrates.  Specifically we constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details appear in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios: first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:

>>>>

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
\label{secTheory}
A pair of bonded silicon wafers or pucks with a small gap forms three coupled cavities with the air gap as the the central cavity.  The axial extent of the silicon cavities are large enough---and typical measurement spectral resolution low enough---that the the Si cavities reflect and transmit light incoherently at their entrance and exit interfaces.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps.  In the air gap, however, the gap size is small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the thick Si substrates.  Specifically we constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details appear in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios: first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:
